---
title: "ReadMe"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## To Do Items
* Fill out vignette
* Fill out ReadMe
* Create package description markdown

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Prioritization Matrix Example

```{r heatmap, warning=FALSE, message=FALSE}
library(priorityMatrix)
priorities <- c("Compelling use case","Affordable and low cost","More convenient")
values <- c("Social Currency","Price","Design","Function","Personal Narrative")
vImport <- c(5,2,2,4,5)
pImport <- c(5,2,3)
createHeatmap()
```

## Evaluating a Business Idea Based on the Prioritization Matrix

```{r evalOption, warning=FALSE, message=FALSE}
optionImportance(priorities)
```
